Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-19 manuscript/manuscript.tex
Improve computation times text in manuscript

We define a $20^\circ \times 20^\circ$ tesseroid of 1km of thickness and a single
computation point located at different heights (0m, 1km, 10km, 100km and 1000km) above
the top surface of the tesseroid.
Then we compute the gravitational potential $V$ and the $g_z$ that the tesseroid
generates on the computation point in case of an homogeneous density, a linear density
and an exponential density with $b = 3$ (Eq.~\ref{eq:density-exp}).
We perform 10000 computations for each field, density and computation height while
tracking the computation time for each one of them.
The final computation time is obtained as the mean value of these runs.

>>>>

We define a $20^\circ \times 20^\circ$ tesseroid of 1km of thickness and a single
computation point located at different heights (1m, 10m, 100m, 1km, 10km, 100km and
1000km) above the top surface of the tesseroid.
Then we compute the gravitational potential $V$ and the $g_z$ that the tesseroid
generates on the computation point in case of an homogeneous density, a linear density
and an exponential density with $b = 3$ (Eq.~\ref{eq:density-exp}).
We perform 1000 computations for each field, density and computation height while
tracking the computation time for each one of them.
The final computation time is obtained as the mean value of these runs.
